Price of Anarchy for Mean Field Games

### 2018-07-15 PoA.tex
just starting second half of proposition 5

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda \to 0$
	and $B \to \infty,\ C^u \to 0,\ D^u \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
	$$ \lambda = \mathcal{O}(\bar{b}^{-1}_2),\ C^u = \mathcal{O}(\bar{b}_2^{-1}),\ D^u = \mathcal{O}(\bar{b}_2^{-1}),\ B = \mathcal{O}(\bar{b}_2^2),$$
	and 
	$$ \frac{\delta^\pm_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\infty,\bar{b}_2}.$$
	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u_t &= \frac{ - \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^+_u}{\sqrt{b_2 + \bar{b}_2}}  \right) + \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^-_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^+_u - \delta^-_u)(T-t)}}{ \left( \frac{\delta^-_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) - \left( \frac{\delta^+_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) 
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, we have $B \cdot u_t = \mathcal{O}\left({\bar{b}_2}^{1/2}\right)$ for $t \in [0,T)$ and 
	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
	As in the proof of Proposition \ref{prop:b2}, for $t \in [0,T)$:
	$$ (b_2 + \bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$$
	so that $w_t \to 0, \forall t \in [0,T)$ as $\bar{b}_2 \to \infty$. Hence, by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty} \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w_t \right)^2 \cdot \left(\bar{x}_t^{MFG} \right)^2 dt \to 0.
	$$	
	Moreover, as shown in the case $\bar{b}_2 \to 0$, $\eta_t$ as well as the variance $v_t$ are invariant w.r.t. $\bar{b}_2$ and $v_t>0$ for $t>0$. Thus,
	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}> 0.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
\end{proof}

>>>>

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
	$$ \lambda^{\bar{b}_2} = \mathcal{O}(\bar{b}^{-1}_2),\ B^{\bar{b}_2} = \mathcal{O}(\bar{b}_2^2),\ C^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),\ D^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),$$
	and 
	$$ \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty}.$$
	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u_t &= \frac{ - \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^+_u}{\sqrt{b_2 + \bar{b}_2}}  \right) + \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^-_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^+_u - \delta^-_u)(T-t)}}{ \left( \frac{\delta^-_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) - \left( \frac{\delta^+_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) 
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, we have $B \cdot u_t = \mathcal{O}\left({\bar{b}_2}^{1/2}\right)$ for $t \in [0,T)$ and 
	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
	As in the proof of Proposition \ref{prop:b2}, for $t \in [0,T)$:
	$$ (b_2 + \bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$$
	so that $w_t \to 0, \forall t \in [0,T)$ as $\bar{b}_2 \to \infty$. Hence, by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty} \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w_t \right)^2 \cdot \left(\bar{x}_t^{MFG} \right)^2 dt \to 0.
	$$	
	Moreover, as shown in the case $\bar{b}_2 \to 0$, $\eta_t$ as well as the variance $v_t$ are invariant w.r.t. $\bar{b}_2$ and $v_t>0$ for $t>0$. Thus,
	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}> 0.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
\end{proof}
